MCC_Preference_Weak

### 2018-05-08 stats/ex3_comparisons.Rmd
adding noisy model predictions and weaker priors

data %>%
  group_by(experiment,alignment,change) %>%
  summarise(n = length(id))
```

@@

plot1 <- data.frame(pd$Experiment[pd$Model=="Data"],pd$mean[pd$Model=="Data"],pd$mean[pd$Model=="Prior only"],rep("Data vs Prior only",8))
names(plot1) = c("Experiment","Data","Model","Comp")
plot2 <- data.frame(pd$Experiment[pd$Model=="Data"],pd$mean[pd$Model=="Data"],pd$mean[pd$Model=="Full model"],rep("Data vs Full model",8))
names(plot2) = c("Experiment","Data","Model","Comp")
plot3 <- data.frame(rep("Combined",8),pd$mean[pd$Model=="Data"],pd$mean[pd$Model=="Full model"],rep("Data vs Full model",8))
names(plot3) = c("Experiment","Data","Model","Comp")
plot4 <- data.frame(rep("Combined",8),pd$mean[pd$Model=="Data"],pd$mean[pd$Model=="Prior only"],rep("Data vs Prior only",8))
names(plot4) = c("Experiment","Data","Model","Comp")

plot <- rbind(plot3,plot4,plot1,plot2)

ggplot(data = plot,aes(x = Model, y = Data, col = Comp)) +
  geom_point()+
  facet_grid(Experiment~Comp)+
  stat_cor(method = "pearson", label.x = 0.4, label.y = 0.9)+
  geom_smooth(method = "lm", se = F, col = "black")+
  theme_few() + 
  guides(col = F)+
  scale_colour_solarized()

@@

@@

filter(bda, Iteration == 1)

posterior.noise <- bda %>%
  filter(Parameter == "noise")%>%
  summarise(noise = mean(value))

posterior.predictive = bda %>%
  filter(Parameter != "noise") %>%
  separate(Parameter, into = c("Experiment", "Change", "Alignment"), sep="_")

ggplot(posterior.predictive, aes(x = value))+
  geom_histogram(binwidth = .01)+
  facet_wrap(~Experiment+Change+Alignment, nrow = 2)

noisy.model <- posterior.predictive %>%
  mutate(Model="Noisy Model")%>%
  group_by(Model,Experiment,Change,Alignment)%>%
  multi_boot_standard(col = "value")

p.com <- bind_rows(noisy.model,pd)

>>>>

data %>%
  group_by(experiment,alignment,change) %>%
  summarise(n = length(id))

@@

plot1 <- data.frame(pd$Experiment[pd$Model=="Data"],pd$mean[pd$Model=="Data"],pd$mean[pd$Model=="Prior only"],rep("Data vs Prior only",8))
names(plot1) = c("Experiment","Data","Model","Comp")
plot2 <- data.frame(pd$Experiment[pd$Model=="Data"],pd$mean[pd$Model=="Data"],pd$mean[pd$Model=="Full model"],rep("Data vs Full model",8))
names(plot2) = c("Experiment","Data","Model","Comp")
plot5 <- data.frame(noisy.model$Experiment,pd$mean[pd$Model=="Data"],noisy.model$mean,rep("Data vs Noisy Model",8))
names(plot5) = c("Experiment","Data","Model","Comp")

plot3 <- data.frame(rep("Combined",8),pd$mean[pd$Model=="Data"],pd$mean[pd$Model=="Full model"],rep("Data vs Full model",8))
names(plot3) = c("Experiment","Data","Model","Comp")
plot4 <- data.frame(rep("Combined",8),pd$mean[pd$Model=="Data"],pd$mean[pd$Model=="Prior only"],rep("Data vs Prior only",8))
names(plot4) = c("Experiment","Data","Model","Comp")

plot <- rbind(plot1,plot2,plot5)

ggplot(data = plot,aes(x = Model, y = Data, col = Comp)) +
  geom_point()+
  facet_grid(~Comp)+
  stat_cor(method = "pearson", label.x = 0.4, label.y = 0.9)+
  geom_smooth(method = "lm", se = F, col = "black")+
  theme_few() + 
  guides(col = F)+
  scale_colour_solarized()

@@

## check one iteration
filter(bda, Iteration == 1)

@@

## distribution of noise
posterior.noise <- bda %>%
  filter(Parameter == "noise")

ggplot(posterior.noise, aes(x = value))+
  geom_histogram()

## distribution of model predictions
posterior.predictive = bda %>%
  filter(Parameter != "noise") %>%
  separate(Parameter, into = c("Experiment", "Change", "Alignment"), sep="_")

ggplot(posterior.predictive, aes(x = value))+
  geom_histogram(binwidth = .01)+
  facet_wrap(~Experiment+Change+Alignment, nrow = 2,scales = 'free')

## Bayesian credible intervals

library(coda)

estimate_mode <- function(s) {
  d <- density(s)
  return(d$x[which.max(d$y)])
}

hdi_upper<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","upper"])
}

hdi_lower<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","lower"])
}

noisy.model <- posterior.predictive %>%
  mutate(Model="Noisy Model")%>%
  group_by(Model,Experiment,Change,Alignment) %>%
  summarise(mean = estimate_mode(value), ci_lower = hdi_lower(value), ci_upper = hdi_upper(value))

## joining noisy model predictions with other predictions
p.com <- bind_rows(noisy.model,pd)

### 2018-05-08 stats/mcc_pref.weak2.Rmd
adding noisy model predictions and weaker priors

## importing data
d <- read_csv(file="pref.weak.data.csv") %>%
  mutate(trial_type = ifelse(trial == "train", "train", "test"))

@@

# maximal converging model
lm <- glmer(correct ~ change + (change |id) + (change |choiceAgent), 
              data = data_cg, family = binomial, 
              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

@@

Conditions by agents. Unequal distribution of agents across change leads to seemingly strange patterns for some agents. However, these strange results are always those with very few data points (e.g. Tiger novelty speaker change is only one data point). For those cells with more than five data points, the pattern is very similar to the overall pattern. Agents are ranodmly selected and assigned to speaker change in the beginning of the experiment. This causes the unequal distribution.
```{r trials per condition and agent}
d %>%
  filter(trial_type == "test") %>%
  mutate(choiceAgent = ifelse( change == "false", agent, altAgent)) %>%
  group_by(choiceAgent,change) %>%
  summarise(n = length(choiceAgent), 
            correct = mean(correct)) %>%
  knitr::kable(digits = 2)
```

>>>>

## importing data
d <- read_csv(file="pref.weak.data2.csv") %>%
  mutate(trial_type = ifelse(trial == "train", "train", "test"))

@@

# maximal converging model
lm <- glmer(correct ~ change + (change |id) + (change || choiceAgent), 
              data = data_cg, family = binomial, 
              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

@@
